A Study of Residual Adapters for Multi-Domain Neural Machine Translation

### 2020-09-02 2020/wmt_20/emnlp2020.tex
post discussion

Because of the limit of our computational resources, we restrict our experiments in this section to the En$\rightarrow$Fr task. Results are in Table~\ref{tab:performance-multi}.

>>>>

Because of the limit of our computational resources, we restrict the experiments in this section to the En$\rightarrow$Fr task. Results are in Table~\ref{tab:performance-multi}.\fyFuture{Perform experiments for de:en}\fyFuture{Restore results where residual are removed from other paper.}
